Web Processing - Standardised GIS Analyses for Cable Route Planning

### 2023-03-14 paper/discussion.tex
grammar, typos

For b), two methods have been used to increase the similarity of the paths computed from the medium resolution raster, to the path of the highest resolution raster.
These methods are used as surrogates for the more complex calculation of the Least Cost Path with the higher resolution.
In the first method a bi-linear downsampling of the higher resolution raster has been applied and in the second method, the all touched set to False and True raster were averaged in different ratios, to compute the optimum weighted cost raster.
While the second method of using an averaged raster, a higher similarity to the path from the highest resolution raster, the downsampling method is simpler and does not need to be optimised for the given cost.
This disadvantage could be reduced by normalising the costs.

>>>>

For b), two methods have been used to increase the similarity of the paths computed from the medium resolution raster, to the path of the highest resolution raster.
These methods are used as surrogates for the more complex calculation of the Least Cost Path with the higher resolution.
In the first method a bi-linear downsampling of the higher resolution raster has been applied and in the second method, the all~touched set to False and True raster were averaged in different ratios, to compute the optimum weighted cost raster.
While the second method of using an averaged raster, a higher similarity to the path from the highest resolution raster, the downsampling method is simpler and does not need to be optimised for the given cost.
This disadvantage could be reduced by normalising the costs.
The fact that downsampling leads to paths that are closer to all~touched True, can be attributed, to the fact, that all objects are included similar to all~touched True.

### 2023-03-14 paper/results.tex
grammar, typos

The opposite is True for the lower resolution raster which is more similar to paths computed from the all~touched True cost raster.
Every path from a downsampled raster is more similar to a path computed from an all~touched set to True raster, than to an all~touched set to False raster, although the all~touched set to False raster of the 5 m resolution was used for downsampling.\todo{interpretation all~touched True and downsampling, both show all details, but downsampling, more similar to original geometry}

>>>>

The opposite is true for the lower resolution raster which is more similar to paths computed from the all~touched True cost raster.
Every path from a downsampled raster is more similar to a path computed from an all~touched set to True raster, than to an all~touched set to False raster, although the all~touched set to False raster of the 5 m resolution was used for downsampling.
